Packaging research artefacts with RO-Crate

### 2021-05-24 latex/ro-crate.tex
Updates from Overleaf
more LaTeX in 80.formal-definition.tex
it does not seem to work with markdown sections though
where have all the DOIs gone..
No need for Iosevko font anymore
ORCID for Marco

% From https://www.overleaf.com/latex/templates/using-the-stix2-opentype-fonts-with-lualatex-or-xelatex/hdfvhzqmhnpx
\usepackage{amsmath}
\usepackage{amssymb}
% \usepackage{hyperref}
\usepackage{fontspec}
\usepackage{unicode-math}
% \usepackage{graphicx}

@@

% https://typeof.net/Iosevka/ mono font has 
% all; the logic symbols we need
\setmonofont{iosevka-slab}[
    Extension={.ttf},
    Path=./ttf-iosevka-slab-6.1.3/,
    Scale=MatchLowercase,
    UprightFont={*-light},
    ItalicFont={*-lightitalic}
]

@@

% Two or more authors:
\author[SSR1,SSR2]{\inits{S.}\fnms{Stian}
    \snm{Soiland-Reyes}\ead[label=eSSR]{soiland-reyes@manchester.ac.uk}\ead[label=oSSR,orcid]{0000-0001-9842-9718}%
    \thanks{Corresponding author. \printead{eSSR}.}}, 
\author[PS]{\inits{P.}\fnms{Peter}
    \snm{Sefton}\ead[label=ePS]{Peter.Sefton@uts.edu.au}\ead[label=oPS,orcid]{0000-0002-3545-944X}},
\author[EOC]{\inits{E.}\fnms{Eoghan}
    \snm{Ó Carragáin}\ead[label=eEOC]{eoghan.ocarragain@ucc.ie}\ead[label=oEOC,orcid]{0000-0001-8131-2150}},
\author[MC]{\inits{M.}\fnms{Mercè}
    \snm{Crosas}\ead[label=eMC]{mcrosas@g.harvard.edu}\ead[label=oMC,orcid]{0000-0003-1304-1939}},
\author[LJC]{\inits{LJ.}\fnms{Leyla Jael}
    \snm{Castro}\ead[label=eLJC]{ljgarcia@zbmed.de}\ead[label=oLJC,orcid]{0000-0003-3986-0510}},
\author[FC]{\inits{F.}\fnms{Frederik}
    \snm{Coppens}\ead[label=eFC]{frcop@psb.vib-ugent.be}\ead[label=oFC,orcid]{0000-0001-6565-5145}},
\author[JMF]{\inits{JM.}\fnms{José M.}
    \snm{Fernández}\ead[label=eJMF]{jose.m.fernandez@bsc.es}\ead[label=oJMF,orcid]{0000-0002-4806-5140}},
\author[DG]{\inits{D.}\fnms{Daniel}
    \snm{Garijo}\ead[label=eDG]{dgarijo@fi.upm.es}\ead[label=oDG,orcid]{0000-0003-0454-7145}},
\author[MLR]{\inits{M.}\fnms{Marco}
    \snm{La Rosa}\ead[label=eMLR]{m@lr.id.au}},
\author[SL]{\inits{S.}\fnms{Simone}
    \snm{Leo}\ead[label=eSL]{simone.leo@crs4.it}\ead[label=oSL,orcid]{0000-0001-8271-5429}},
\author[MP]{\inits{M.}\fnms{Marc}
    \snm{Portier}\ead[label=eMP]{marc.portier@vliz.be}\ead[label=oMP,orcid]{0000-0002-9648-6484}},
\author[AT]{\inits{A.}\fnms{Ana}
    \snm{Trisovic}\ead[label=eMP]{ana.trisovic@gmail.com}\ead[label=oAT,orcid]{0000-0003-1991-0533}},
\author[RO]{RO-Crate Community},
\author[PG]{\inits{P.}\fnms{Paul}
    \snm{Groth}\ead[label=ePG]{p.t.groth@uva.nl}\ead[label=oPG,orcid]{0000-0003-0183-6910}},
\author[CG]{\inits{C.}\fnms{Carole}
    \snm{Goble}\ead[label=eCG]{carole.goble@manchester.ac.uk}\ead[label=oCG,orcid]{0000-0003-1219-2137}}

\address[SSR1]{Computer Science, 
    \orgname{The University of Manchester}, \cny{UK}}
\address[SSR2]{Informatics Institute, \orgname{University of Amsterdam},
    \cny{The Netherlands}\printead[presep={\\}]{eSSR,oSSR}}
\address[PS]{Faculty of Science, \orgname{University Technology Sydney},
    \cny{Australia}\printead[presep={\\}]{ePS,oPS}}
\address[EOC]{\orgname{University College Cork},
    \cny{Ireland}\printead[presep={\\}]{oEOC}}
\address[MC]{Institute for Quantitative Social Science, 
    \orgname{Harvard University}, Cambridge, MA,  \cny{USA}\printead[presep={\\}]{oMC}}
\address[LJC]{\orgname{ZB MED Information Centre for Life Sciences}, 
    Cologne, \cny{Germany}\printead[presep={\\}]{oLJC}}
\address[FC]{\orgname{VIB-UGent Center for Plant Systems Biology}, 
    Gent, \cny{Belgium}\printead[presep={\\}]{oFC}}
\address[JMF]{\orgname{Barcelona Supercomputing Center}, 
    Barcelona, \cny{Spain}\printead[presep={\\}]{oJMF}}
\address[DG]{Ontology Engineering Group, 
    \orgname{Universidad Politécnica de Madrid}, Madrid, \cny{Spain}\printead[presep={\\}]{oDG}}
\address[MLR]{\printead{eMLR}}
\address[SL]{\orgname{Center for Advanced Studies, Research, and Development in Sardinia} (CRS4), Pula (CA),
    \cny{Italy}\printead[presep={\\}]{oSL}}
\address[MP]{\orgname{Vlaams Instituut voor de Zee}, Oostende,
    \cny{Belgium}\printead[presep={\\}]{oMP}}
\address[AT]{Institute for Quantitative Social Science,
    \orgname{Harvard University}, Cambridge, MA, \cny{USA}\printead[presep={\\}]{oAT}}
\address[RO]{\url{https://www.researchobject.org/ro-crate/community} (see appendix B)}
\address[PG]{Informatics Institute, \orgname{University of Amsterdam},
    \cny{The Netherlands}\printead[presep={\\}]{ePG,oPG}}
\address[CG]{Computer Science, \orgname{The University of Manchester},
    \cny{UK}\printead[presep={\\}]{eCG,oCG}}

@@

\markdownInput{../content/40.inuse.md}
\markdownInput{../content/41.workflows.md}
\markdownInput{../content/42.regulatory.md}
\markdownInput{../content/43.culturalheritage.md}
\markdownInput{../content/44.dmp.md}

@@

\appendix
\markdownInput{../content/80.formal-definition.md}
% TODO: Recode formal definition to LaTeX math mode?
%\include{../content/80.formal-definition}

>>>>

% From https://www.overleaf.com/latex/templates/using-the-stix2-opentype-fonts-with-lualatex-or-xelatex/hdfvhzqmhnpx
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{xcolor}
\definecolor{darkerblue}{cmyk}{1,1,0,0.45}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    citecolor=black,
    urlcolor=darkerblue}

\usepackage{fontspec}
\usepackage{unicode-math}
% \usepackage{graphicx}

% Hyperlinks on DOI permalinks – just 20 years after DOI invention!
% 
% We had to make our own copy of 
% https://ctan.org/pkg/doi?lang=en 
% where commands are renamde to \doix
% because iosart2x.cls and ios1.bst have 
% a different use of \doiurl \doi etc.
% We also set the doixtext prefix empty
% to avoid doi:doi:
\usepackage{doix}
\renewcommand{\doixtext}{}
\renewcommand{\doiurl}[1]{\doix{#1}}

@@

% https://typeof.net/Iosevka/ mono font has 
% all; the logic symbols we need
%\setmonofont{iosevka-slab}[
%    Extension={.ttf},
%    Path=./ttf-iosevka-slab-6.1.3/,
%    Scale=MatchLowercase,
%    UprightFont={*-light},
%    ItalicFont={*-lightitalic}
%]

@@

% Two or more authors:
\author[SSR1,SSR2]{\inits{S.}\fnms{Stian}
    \snm{Soiland-Reyes}\ead[label=eSSR]{soiland-reyes@manchester.ac.uk}\ead[label=oSSR,orcid]{0000-0001-9842-9718}%
    \thanks{Corresponding author. \printead{eSSR}.}}, 
\author[PS]{\inits{P.}\fnms{Peter}
    \snm{Sefton}\ead[label=ePS]{Peter.Sefton@uts.edu.au}\ead[label=oPS,orcid]{0000-0002-3545-944X}},
\author[EOC]{\inits{E.}\fnms{Eoghan}
    \snm{Ó Carragáin}\ead[label=eEOC]{eoghan.ocarragain@ucc.ie}\ead[label=oEOC,orcid]{0000-0001-8131-2150}},
\author[MC]{\inits{M.}\fnms{Mercè}
    \snm{Crosas}\ead[label=eMC]{mcrosas@g.harvard.edu}\ead[label=oMC,orcid]{0000-0003-1304-1939}},
\author[LJC]{\inits{LJ.}\fnms{Leyla Jael}
    \snm{Castro}\ead[label=eLJC]{ljgarcia@zbmed.de}\ead[label=oLJC,orcid]{0000-0003-3986-0510}},
\author[FC]{\inits{F.}\fnms{Frederik}
    \snm{Coppens}\ead[label=eFC]{frcop@psb.vib-ugent.be}\ead[label=oFC,orcid]{0000-0001-6565-5145}},
\author[JMF]{\inits{JM.}\fnms{José M.}
    \snm{Fernández}\ead[label=eJMF]{jose.m.fernandez@bsc.es}\ead[label=oJMF,orcid]{0000-0002-4806-5140}},
\author[DG]{\inits{D.}\fnms{Daniel}
    \snm{Garijo}\ead[label=eDG]{dgarijo@fi.upm.es}\ead[label=oDG,orcid]{0000-0003-0454-7145}},
\author[MLR]{\inits{M.}\fnms{Marco}
    \snm{La Rosa}\ead[label=eMLR]{m@lr.id.au}\ead[label=oMLR,orcid]{0000-0001-5383-6993}},
\author[SL]{\inits{S.}\fnms{Simone}
    \snm{Leo}\ead[label=eSL]{simone.leo@crs4.it}\ead[label=oSL,orcid]{0000-0001-8271-5429}},
\author[MP]{\inits{M.}\fnms{Marc}
    \snm{Portier}\ead[label=eMP]{marc.portier@vliz.be}\ead[label=oMP,orcid]{0000-0002-9648-6484}},
\author[AT]{\inits{A.}\fnms{Ana}
    \snm{Trisovic}\ead[label=eMP]{ana.trisovic@gmail.com}\ead[label=oAT,orcid]{0000-0003-1991-0533}},
\author[RO]{RO-Crate Community},
\author[PG]{\inits{P.}\fnms{Paul}
    \snm{Groth}\ead[label=ePG]{p.t.groth@uva.nl}\ead[label=oPG,orcid]{0000-0003-0183-6910}},
\author[CG]{\inits{C.}\fnms{Carole}
    \snm{Goble}\ead[label=eCG]{carole.goble@manchester.ac.uk}\ead[label=oCG,orcid]{0000-0003-1219-2137}}

\address[SSR1]{Computer Science, 
    \orgname{The University of Manchester}, \cny{UK}}
\address[SSR2]{Informatics Institute, \orgname{University of Amsterdam},
    \cny{The Netherlands}\printead[presep={\\}]{eSSR,oSSR}}
\address[PS]{Faculty of Science, \orgname{University Technology Sydney},
    \cny{Australia}\printead[presep={\\}]{ePS,oPS}}
\address[EOC]{\orgname{University College Cork},
    \cny{Ireland}\printead[presep={\\}]{oEOC}}
\address[MC]{Institute for Quantitative Social Science, 
    \orgname{Harvard University}, Cambridge, MA,  \cny{USA}\printead[presep={\\}]{oMC}}
\address[LJC]{\orgname{ZB MED Information Centre for Life Sciences}, 
    Cologne, \cny{Germany}\printead[presep={\\}]{oLJC}}
\address[FC]{\orgname{VIB-UGent Center for Plant Systems Biology}, 
    Gent, \cny{Belgium}\printead[presep={\\}]{oFC}}
\address[JMF]{\orgname{Barcelona Supercomputing Center}, 
    Barcelona, \cny{Spain}\printead[presep={\\}]{oJMF}}
\address[DG]{Ontology Engineering Group, 
    \orgname{Universidad Politécnica de Madrid}, Madrid, \cny{Spain}\printead[presep={\\}]{oDG}}
\address[MLR]{\printead{oMLR}}
\address[SL]{\orgname{Center for Advanced Studies, Research, and Development in Sardinia} (CRS4), Pula (CA),
    \cny{Italy}\printead[presep={\\}]{oSL}}
\address[MP]{\orgname{Vlaams Instituut voor de Zee}, Oostende,
    \cny{Belgium}\printead[presep={\\}]{oMP}}
\address[AT]{Institute for Quantitative Social Science,
    \orgname{Harvard University}, Cambridge, MA, \cny{USA}\printead[presep={\\}]{oAT}}
\address[RO]{\url{https://www.researchobject.org/ro-crate/community} (see appendix B)}
\address[PG]{Informatics Institute, \orgname{University of Amsterdam},
    \cny{The Netherlands}\printead[presep={\\}]{ePG,oPG}}
\address[CG]{Computer Science, \orgname{The University of Manchester},
    \cny{UK}\printead[presep={\\}]{eCG,oCG}}

@@

\markdownInput{../content/40.inuse.md}
\markdownInput{../content/41.workflows.md}
\markdownInput{../content/42.regulatory.md}
\markdownInput{../content/43.culturalheritage.md}
\markdownInput{../content/44.dmp.md}
\markdownInput{../content/45.institutional-repos.md}

@@

\appendix
%\markdownInput{../content/80.formal-definition.md}
\input{../content/80.formal-definition}
